Constant-sized correlations are sufficient for robust self-testing of maximally entangled states with unbounded dimension

### 2019-05-03 Draft/draft.tex
Honghao: edits of section 6

The full correlation, denoted by $\fC(d,r)$, is generated by the ideal strategy that can pass all the three tests. We give the ideal strategy first.
%--------------------------------------------
\subsection{The ideal strategy}
%--------------------------------------------
Recall the two subspaces $W_{d-1}$ and $W_2$ defined in \cref{eq:w_subspace}. 
In the ideal strategy Alice and Bob share the state 
\begin{align*}
\ket{\psi} = &\frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j}\ket{x_{d-j}}\right)\\
=&\frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(1/\sqrt{d-1} \sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j})\right).
\end{align*}
Here we introduce the second basis $\{ \ket{j} \}_{j=1}^{d-1}$ of $W_{d-1}$ so that
the observables used in the extended weighted CHSH test have a simpler form.
The two basis are related by
\begin{align*}
	\ket{x_j} = \frac{-1}{\sqrt{2}}(\ket{j} + i\ket{d-j}), &&
	\ket{x_{d-j}} = \frac{-e^{ij\pi/d}}{\sqrt{2}}(\ket{j} - i\ket{d-j}) && \text{for } j = 1 \dots \frac{d-1}{2}.
\end{align*}
We define two subspaces $V = \spn\{\ket{1}, \ket{d-1}\}$ and $V^\perp = W_{d-1} \setminus\spn\{\ket{1}, \ket{d-1}\}$ on
$W_{d-1}$ and
define $\Pi_V$ and $\Pi_{V^\perp}$ to be the corresponding projectors. Note that $V$ is the subspace on which they should maximize $\ip{\I_{\cot(-\pi/d)}}$.
We define the states for the measurements used in the extended weighted CHSH test as follows
\begin{align*}
	&\ket{1_+} = \cos(-\frac{\pi}{2d})\ket{1} + \sin(-\frac{\pi}{2d})\ket{d-1}
	&&\ket{(d-1)_+} = \sin(-\frac{\pi}{2d})\ket{1} - \cos(-\frac{\pi}{2d})\ket{d-1}\\
	&\ket{1_-} = \cos(-\frac{\pi}{2d})\ket{1} - \sin(-\frac{\pi}{2d})\ket{d-1}
	&&\ket{(d-1)_-} = \sin(-\frac{\pi}{2d})\ket{1} + \cos(-\frac{\pi}{2d})\ket{d-1}\\
	&\ket{1_{\times}} = \frac{1}{\sqrt{2}}\ket{1} + \frac{1}{\sqrt{2}}\ket{d-1}
	&&\ket{(d-1)_{\times}} = \frac{1}{\sqrt{2}}\ket{1} - \frac{1}{\sqrt{2}}\ket{d-1}.
\end{align*}
Then the measurements are
\begin{align*}
	&M_\ast^\diamond =(\1_{W_2})^{\x 2} \x \Pi_V && M_\ast^\perp = M_{n+1}^\perp = M_{n+2}^\perp = (\1_{W_2})^{\x 2} \x \Pi_{V^\perp}\\
	&N_\ast^\diamond = (\1_{W_2})^{\x 2} \x \Pi_V && N_\ast^\perp = N_{n+1}^\perp = N_{n+2}^\perp = (\1_{W_2})^{\x 2} \x \Pi_{V^\perp}\\
	&M_{n+1}^0 =N_{n+1}^0=(\1_{W_2})^{\x 2} \x  \ketbra{1}{1} && M_{n+1}^1=N_{n+1}^1 = (\1_{W_2})^{\x 2} \x \ketbra{d-1}{d-1}\\
	&M_{n+2}^0 =N_{n+2}^0=(\1_{W_2})^{\x 2} \x  \ketbra{1_{\times}}{1_{\times}} && M_{n+2}^1= N_{n+2}^1 = (\1_{W_2})^{\x 2} \x \ketbra{(d-1)_{\times}}{(d-1)_{\times}}\\
	&M_1^0 = N_1^0 =(\1_{W_2})^{\x 2} \x  \ketbra{1_+}{1_+} && M_1^1 = N_1^1 =(\1_{W_2})^{\x 2} \x  \ketbra{(d-1)_+}{(d-1)_+}\\
	&M_2^0 = N_2^0 = (\1_{W_2})^{\x 2} \x \ketbra{1_-}{1_-} && M_1^1 = N_1^1 = (\1_{W_2})^{\x 2} \x \ketbra{(d-1)_-}{(d-1)_-}.
\end{align*}
The observables for $\LS(\Gamma_r)$ are
\begin{align}
	M_i = N_i = \Psi(x_i),
\end{align}
where the representation $\Psi$ is defined in \cref{def:rep_gamma}.
Note that Alice uses the same observable for the same variable appearing in different equations.

@@

The other relations that are embedded in $\Gamma_r$ are 
\begin{align}
	\label{eq:comm}&[f_0, a_i] = [f_2, a_i] = [g_0, a_i] = [g_2, a_i] = e \text{ for all } i = 1 \dots r+5 \\
	\label{eq:mg1}&f_0g_0 = Jg_0f_0 \\
	\label{eq:mg2}&f_2g_2 = J g_2 f_2.
\end{align}
We summarize the implications in the following proposition.
\begin{proposition}
	\label{prop:lct_comm}
	Let $S$, $\{M_j, N_j\}_{j=1}^{\nr}$ be the strategy and observables defined in \cref{prop:lct_base},
	then
	\begin{align}
		&M_{r+6} M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+6} \ket{\psi} && 
		M_{r+8}M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+8} \ket{\psi} \\
		&M_{r+9} M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+9} \ket{\psi} && 
		M_{r+11}M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+11} \ket{\psi} 
	\end{align}
	for all $j = 1 \dots r+5$, and
	\begin{align}
		&M_{r+6}M_{r+9} \ket{\psi} \appd{O(r\se)} - M_{r+9}M_{r+6} \ket{\psi} \\
		&M_{r+8}M_{r+11} \ket{\psi} \appd{O(r\se)} -M_{r+11}M_{r+8} \ket{\psi}.
	\end{align}
\end{proposition}
Recall all the relations in \cref{eq:comm,eq:mg1,eq:mg2} are embedded in constant number of linear relations in $\Gamma_r$,
so this proposition can be proved using the same technique used in the proof of \cref{prop:lct_base}.
%------------------------------------------------------------------------------------------
\subsection{Implication of passing the extended weighted CHSH test}
\label{sec:imp_chsh}
%------------------------------------------------------------------------------------------
\begin{proposition}
\label{prop:chsh_base}
Let $S$ be an $\ep$-approximate quantum strategy,
then the strategy $S$ satisfy the following relations
\begin{align}
	  M_\ast^\diamond N_\ast^\diamond \ket{\psi}
	  \appd{O( r\se)}&M_\ast^\diamond \ket{\psi} \appd{O( r\se)} (M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \appd{O( r\se)} (M_{\nr+2}^0+M_{\nr+2}^1)\ket{\psi} \\
	  \appd{O( r\se)}&N_\ast^\diamond \ket{\psi} \appd{O( r\se)} (N_{\nr+1}^0+N_{\nr+1}^1)\ket{\psi} \appd{O( r\se)} (N_{\nr+2}^0+N_{\nr+2}^1)\ket{\psi}\\
	M_\ast^\perp N_\ast^\perp\ket{\psi}\appd{O( r\se)} &M_\ast^\perp\ket{\psi} \appd{O( r\se)} M_{\nr+1}^\perp \ket{\psi} \appd{O( r\se)} M_{\nr+2}^\perp \ket{\psi}\\
	\appd{O( r\se)}&N_\ast^\perp\ket{\psi} \appd{O( r\se)} N_{\nr+1}^\perp \ket{\psi} \appd{O( r\se)} N_{\nr+2}^\perp \ket{\psi}.
\end{align}
and
\begin{align}
&M_{\nr+1}^0 \ket{\psi} \appd{O( r\se)} N_{\nr+1}^0 \ket{\psi} && M_{\nr+1}^1\ket{\psi} \appd{O( r\se)} N_{\nr+1}^1 \ket{\psi}\\
&M_{\nr+2}^0 \ket{\psi} \appd{O( r\se)} N_{\nr+2}^0 \ket{\psi} && M_{\nr+2}^1\ket{\psi} \appd{O( r\se)} N_{\nr+2}^1 \ket{\psi}.
\end{align}
\end{proposition}

@@

%Maybe we can first conclude that $\spn(A_0^0+A_0^1) = \spn(A_1^0+A_1^1) = \spn(A_\ast^\diamond)$.
	\label{prop:s1s2}
	Let $S$ be an $\ep$-approximate strategy. We define
		&M_{\nr+1} = M_{\nr+1}^0 - M_{\nr+1}^1 && M_{\nr+2} = M_{\nr+2}^0 - M_{\nr+2}^1,\\
		&N_{\nr+1} = N_{\nr+1}^0 - N_{\nr+1}^1 && N_{\nr+2} = N_{\nr+2}^0 - N_{\nr+2}^1.
	Then $S$ induces two strategies that achieve $\ip{\I_{\cot(-\pi/d)}}_{\max} - O(d r\se)$, which are
		S_1 = \left(M_{\nr+1}, M_{\nr+2}, N_1, N_2, \frac{M_\ast^\diamond\ket{\psi}}{\norm{M_\ast^\diamond\ket{\psi}}}\right),\\
		S_2 = \left(N_{\nr+1}, N_{\nr+2}, M_1, M_2, \frac{M_\ast^\diamond\ket{\psi}}{\norm{M_\ast^\diamond\ket{\psi}}}\right).

@@

We will prove that $\bra{\psi} M_{\nr+1}^0N_1^0 \ket{\psi} \appd{O(\sd r\se)} \bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi}$ as an example,

@@

	   \bra{\psi} M_{\nr+1}^0N_1^0 \ket{\psi} 
	= &\bra{\psi}(M_\ast^\diamond + M_\ast^\perp) M_{\nr+1}^0N_1^0 (M_\ast^\diamond + M_\ast^\perp)\ket{\psi} \\
	= & \bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi} + \bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\perp\ket{\psi}\\
	&+\bra{\psi}M_\ast^\perp M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi} + \bra{\psi}M_\ast^\perp M_{\nr+1}^0N_1^0 M_\ast^\perp\ket{\psi}\\
	\appd{O(r\se)}&  \bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi} + \bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_{\nr+1}^\perp\ket{\psi} \\
	&+\bra{\psi}M_{\nr+1}^\perp M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi} + \bra{\psi}M_{\nr+1}^\perp M_{\nr+1}^0N_1^0 M_{\nr+1}^\perp\ket{\psi}\\
	=&\bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi},

@@

where we use the facts that $M_\ast^\perp \ket{\psi} \appd{O(r\se)} M_{\nr+1}^\perp \ket{\psi}$ and that 
$\supp(M_{\nr+1}^0) \cap \supp(M_{\nr+1}^\perp) = \emptyset$. This means that if Alice and Bob share state $M_\ast^\diamond \ket{\psi}/\norm{M_\ast^\diamond \ket{\psi}}$ and apply $M_{\nr+1}^0N_1^0$
we get conditional probability

@@

@@

	Let $S$ be an $\ep$-approximate strategy and $M_{\nr+1}, M_{\nr+2},N_{\nr+1}$ and $N_{\nr+2}$ as defined in \cref{prop:s1s2}.

@@

	\textbf{To prove \cref{eq:psi1_eq}}, 
	recall that $M_{\nr+1}^0 \ket{\psi} \appd{O(r\se)} N_{\nr+1}^0 \ket{\psi}$ 
	and $M_{\nr+1}^1 \ket{\psi} \appd{O(r\se)} N_{\nr+1}^1 \ket{\psi}$ proved in \cref{prop:chsh_base},
	so it suffices to show
	$(M_{\nr+2}M_{\nr+1}^1 - M_{\nr+2}M_{\nr+1}^0) \ket{\psi}$ is close to $(- N_{\nr+2}N_{\nr+1}^1+N_{\nr+2}N_{\nr+1}^0)\ket{\psi}$,
	or equivalently,
	$M_{\nr+2}M_{\nr+1} \ket{\psi}$ is close to $-N_{\nr+2}N_{\nr+1} \ket{\psi}$.

	At this point, we use the anticommutation relation induced by $S_1$ (\cref{eq:zaxa}) and conclude that 
	\begin{align}
		M_{\nr+1}M_{\nr+2} M_\ast^\diamond \ket{\psi} \appd{\frac{\norm{\ket{M_\ast^\diamond\ket{\psi}}}}{c\sqrt{s}}O(\sd\sr\qe)} -M_{\nr+1}M_{\nr+2} M_\ast^\diamond \ket{\psi}.
	\end{align}
	If we use the fact $c = 1 - \pi^2/(2d^2) + O(1/d^4)$ and $s = \pi/d + O(1/d^3)$, the distance above is of order $O(\sd \sr \qe)$.
	Then we can show that 
	\begin{align*}
		M_{\nr+2}M_{\nr+1}\ket{\psi} &= M_{\nr+2}M_{\nr+1}(M_{\nr+1}^0 + M_{\nr+1}^1)\ket{\psi} \\
			&\appd{O(r\se)} M_{\nr+2}M_{\nr+1} M_\ast^\diamond \ket{\psi} \\
			&\appd{O(\sd \sr \qe)} -M_{\nr+1}M_{\nr+2} M_\ast^\diamond \ket{\psi}\\
			&\appd{O(r\se)} -M_{\nr+1}M_{\nr+2} \ket{\psi} \\
			&\appd{O(r\se)} -M_{\nr+1} N_{\nr+2} \ket{\psi} \\
			&\appd{O(r\se)} -N_{\nr+2} N_{\nr+1} \ket{\psi}.
	\end{align*}
	The proof of $\ket{\psi_2} \appd{O(\sd \sr \qe)} \ket{\psi_4}$ is similar.

	\textbf{To prove \cref{eq:psi1_sum}}, we use the definition of $\ket{\psi_1}$ and $\ket{\psi_2}$
	\begin{align}
		\ket{\psi_2} + \ket{\psi_1} = 1/2( 2M_{\nr+1}^0 + 2M_{\nr+1}^1) \ket{\psi} \appd{O(r\se)} M_\ast^\diamond \ket{\psi}.
	\end{align}

	\textbf{To prove \cref{eq:psi1_orth}}, we expand the inner product
	\begin{align*}
		&\braket{\psi_1}{\psi_2}\\
	 = &1/4\bra{\psi}(M_{\nr+1}^0 - iM_{\nr+1}^1M_{\nr+2} + iM_{\nr+1}^0M_{\nr+2} +M_{\nr+1}^1)\\
	 &(M_{\nr+1}^1 + iM_{\nr+2}M_{\nr+1}^0 -iM_{\nr+2}M_{\nr+1}^1 + M_{\nr+1}^0)\ket{\psi}\\
	 =& 1/2i \bra{\psi}(M_{\nr+1}^0M_{\nr+2}M_{\nr+1}^0-M_{\nr+1}^1M_{\nr+2}M_{\nr+1}^1\ket{\psi}.
	\end{align*}
	Then we will show that $\bra{\psi} M_{\nr+1}^0M_{\nr+2}M_{\nr+1}^0 \ket{\psi} \appd{O( r\se)} 0$ as follows
	\begin{align*}
	 \bra{\psi}(M_{\nr+1}^0M_{\nr+2}M_{\nr+1}^0\ket{\psi} &\appd{O(r\se)}  \bra{\psi}(N_{\nr+1}^0M_{\nr+2}N_{\nr+1}^0)\ket{\psi}\\
	  &=\bra{\psi}M_{\nr+2}N_{\nr+1}^0)\ket{\psi}\\
	&\appd{O(r^2\ep)} 0,
	\end{align*}
	where the last approximation comes from the correlation.
	Similarly, we have 
	\begin{align*}
	\bra{\psi}(M_{\nr+1}^1M_{\nr+2}M_{\nr+1}^1\ket{\psi} \appd{O(r\se)} \bra{\psi} M_{\nr+2}N_{\nr+1}^1 \ket{\psi} \appd{O(r^2\ep)} 0.
	\end{align*}
	Hence, $\braket{\psi_2}{\psi_1} \appd{O(r\se)} 0$.

@@

        		&= (\cos(2\pi/d) M_{\nr+1}^0 - \sin(2\pi/d) M_{\nr+2}M_{\nr+1}^1)\ket{\psi}.

@@

        		&= (\cos(2\pi/d) M_{\nr+1}^1 + \sin(2\pi/d) M_{\nr+2}M_{\nr+1}^0)\ket{\psi},

@@

We use this observation in the proof of the following proposition.

@@

where $\log_r j$ is the discrete log.

>>>>

In the full test, the question pairs from the three subtests are given to Alice and Bob with equal probability.
The full correlation, denoted by $\fC(d,r)$, is generated by the ideal strategy that can pass all the three tests. We give the ideal strategy first.
%--------------------------------------------
\subsection{The ideal strategy}
%--------------------------------------------
Recall the two subspaces $W_{d-1}$ and $W_2$ defined in \cref{eq:w_subspace}. 
In the ideal strategy Alice and Bob share the state 
\begin{align*}
\ket{\psi} = &\frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(\frac{1}{\sqrt{d-1}} \sum_{j=1}^{d-1} \ket{x_j}\ket{x_{d-j}}\right)\\
=&\frac{1}{2} (\ket{x_1}\ket{x_1} + \ket{x_2}\ket{x_2})^{\x 2} \x \left(1/\sqrt{d-1} \sum_{j=1}^{(d-1)/2} e^{ij\pi/d}(\ket{j}\ket{j} + \ket{d-j}\ket{d-j})\right).
\end{align*}
Here we introduce the second basis $\{ \ket{j} \}_{j=1}^{d-1}$ of $W_{d-1}$ so that
the observables used in the extended weighted CHSH test have a simpler form.
The two basis are related by
\begin{align*}
	\ket{x_j} = \frac{-1}{\sqrt{2}}(\ket{j} + i\ket{d-j}), &&
	\ket{x_{d-j}} = \frac{-e^{ij\pi/d}}{\sqrt{2}}(\ket{j} - i\ket{d-j}) && \text{for } j = 1 \dots \frac{d-1}{2}.
\end{align*}
We define two subspaces $V = \spn\{\ket{1}, \ket{d-1}\}$ and $V^\perp = W_{d-1} \setminus\spn\{\ket{1}, \ket{d-1}\}$ on
$W_{d-1}$ and
define $\Pi_V$ and $\Pi_{V^\perp}$ to be the corresponding projectors. Note that $V$ is the subspace on which they should maximize $\ip{\I_{\cot(-\pi/d)}}$.
We define the states for the measurements used in the extended weighted CHSH test as follows
\begin{align*}
	&\ket{1_+} = \cos(-\frac{\pi}{2d})\ket{1} + \sin(-\frac{\pi}{2d})\ket{d-1}
	&&\ket{(d-1)_+} = \sin(-\frac{\pi}{2d})\ket{1} - \cos(-\frac{\pi}{2d})\ket{d-1}\\
	&\ket{1_-} = \cos(-\frac{\pi}{2d})\ket{1} - \sin(-\frac{\pi}{2d})\ket{d-1}
	&&\ket{(d-1)_-} = \sin(-\frac{\pi}{2d})\ket{1} + \cos(-\frac{\pi}{2d})\ket{d-1}\\
	&\ket{1_{\times}} = \frac{1}{\sqrt{2}}\ket{1} + \frac{1}{\sqrt{2}}\ket{d-1}
	&&\ket{(d-1)_{\times}} = \frac{1}{\sqrt{2}}\ket{1} - \frac{1}{\sqrt{2}}\ket{d-1}.
\end{align*}
Then the measurements are
\begin{align*}
	&M_\ast^\diamond =(\1_{W_2})^{\x 2} \x \Pi_V && M_\ast^\perp = M_{n+1}^\perp = M_{n+2}^\perp = (\1_{W_2})^{\x 2} \x \Pi_{V^\perp}\\
	&N_\ast^\diamond = (\1_{W_2})^{\x 2} \x \Pi_V && N_\ast^\perp = N_{n+1}^\perp = N_{n+2}^\perp = (\1_{W_2})^{\x 2} \x \Pi_{V^\perp}\\
	&M_{n+1}^0 =N_{n+1}^0=(\1_{W_2})^{\x 2} \x  \ketbra{1}{1} && M_{n+1}^1=N_{n+1}^1 = (\1_{W_2})^{\x 2} \x \ketbra{d-1}{d-1}\\
	&M_{n+2}^0 =N_{n+2}^0=(\1_{W_2})^{\x 2} \x  \ketbra{1_{\times}}{1_{\times}} && M_{n+2}^1= N_{n+2}^1 = (\1_{W_2})^{\x 2} \x \ketbra{(d-1)_{\times}}{(d-1)_{\times}}\\
	&M_1^0 = N_1^0 =(\1_{W_2})^{\x 2} \x  \ketbra{1_+}{1_+} && M_1^1 = N_1^1 =(\1_{W_2})^{\x 2} \x  \ketbra{(d-1)_+}{(d-1)_+}\\
	&M_2^0 = N_2^0 = (\1_{W_2})^{\x 2} \x \ketbra{1_-}{1_-} && M_1^1 = N_1^1 = (\1_{W_2})^{\x 2} \x \ketbra{(d-1)_-}{(d-1)_-}.
\end{align*}
The observables for $\LS(\Gamma_r)$ are
\begin{align}
	M_i = N_i = \Psi(x_i),
\end{align}
where the representation $\Psi$ is defined in \cref{def:rep_gamma}.
Note that Alice uses the same observable for the same variable appearing in different equations.

@@

The other relations that are embedded in $\Gamma_r$ are 
\begin{align}
	\label{eq:comm}&[f_0, a_i] = [f_2, a_i] = [g_0, a_i] = [g_2, a_i] = e \text{ for all } i = 1 \dots r+5 \\
	\label{eq:mg1}&f_0g_0 = Jg_0f_0 \\
	\label{eq:mg2}&f_2g_2 = J g_2 f_2.
\end{align}
We summarize the implications in the following proposition.
\begin{proposition}
	\label{prop:lct_comm}
	Let $S$, $\{M_j, N_j\}_{j=1}^{\nr}$ be the strategy and observables defined in \cref{prop:lct_base},
	then
	\begin{align}
		&M_{r+6} M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+6} \ket{\psi} && 
		M_{r+8}M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+8} \ket{\psi} \\
		&M_{r+9} M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+9} \ket{\psi} && 
		M_{r+11}M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+11} \ket{\psi} 
	\end{align}
	for all $j = 1 \dots r+5$, and
	\begin{align}
		&M_{r+6}M_{r+9} \ket{\psi} \appd{O(r\se)} - M_{r+9}M_{r+6} \ket{\psi} \\
		&M_{r+8}M_{r+11} \ket{\psi} \appd{O(r\se)} -M_{r+11}M_{r+8} \ket{\psi}.
	\end{align}
\end{proposition}
Recall all the relations in \cref{eq:comm,eq:mg1,eq:mg2} are embedded in constant number of linear relations in $\Gamma_r$,
so this proposition can be proved using the same technique used in the proof of \cref{prop:lct_base}.
%------------------------------------------------------------------------------------------
\subsection{Implication of passing the extended weighted CHSH test}
\label{sec:imp_chsh}
%------------------------------------------------------------------------------------------
In this subsection, we prove a series of propositions and lemmas which lead to a key result that will be
used in the self-testing proof.
\begin{proposition}
\label{prop:chsh_base}
Let $S$ be an $\ep$-approximate quantum strategy of $\fC(d,r)$,
then the strategy $S$ satisfy the following relations
\begin{align}
	  M_\ast^\diamond N_\ast^\diamond \ket{\psi}
	  \appd{O( r\se)}&M_\ast^\diamond \ket{\psi} \appd{O( r\se)} (M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \appd{O( r\se)} (M_{\nr+2}^0+M_{\nr+2}^1)\ket{\psi} \\
	  \appd{O( r\se)}&N_\ast^\diamond \ket{\psi} \appd{O( r\se)} (N_{\nr+1}^0+N_{\nr+1}^1)\ket{\psi} \appd{O( r\se)} (N_{\nr+2}^0+N_{\nr+2}^1)\ket{\psi}\\
	M_\ast^\perp N_\ast^\perp\ket{\psi}\appd{O( r\se)} &M_\ast^\perp\ket{\psi} \appd{O( r\se)} M_{\nr+1}^\perp \ket{\psi} \appd{O( r\se)} M_{\nr+2}^\perp \ket{\psi}\\
	\appd{O( r\se)}&N_\ast^\perp\ket{\psi} \appd{O( r\se)} N_{\nr+1}^\perp \ket{\psi} \appd{O( r\se)} N_{\nr+2}^\perp \ket{\psi}.
\end{align}
and
\begin{align}
&M_{\nr+1}^0 \ket{\psi} \appd{O( r\se)} N_{\nr+1}^0 \ket{\psi} && M_{\nr+1}^1\ket{\psi} \appd{O( r\se)} N_{\nr+1}^1 \ket{\psi}\\
&M_{\nr+2}^0 \ket{\psi} \appd{O( r\se)} N_{\nr+2}^0 \ket{\psi} && M_{\nr+2}^1\ket{\psi} \appd{O( r\se)} N_{\nr+2}^1 \ket{\psi}.
\end{align}
\end{proposition}

@@

%Maybe we can first conclude that $\spn(A_0^0+A_0^1) = \spn(A_1^0+A_1^1) = \spn(A_\ast^\diamond)$.
\begin{proposition}
	\label{prop:s1s2}
	Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$. We define
	\begin{align}
		&M_{\nr+1} = M_{\nr+1}^0 - M_{\nr+1}^1  && 
		M_{\nr+2} = M_{\nr+2}^0 - M_{\nr+2}^1,\\
		&N_{\nr+1} = N_{\nr+1}^0 - N_{\nr+1}^1  && 
		N_{\nr+2} = N_{\nr+2}^0 - N_{\nr+2}^1.
	\end{align}
	Then $S$ induces two strategies that achieve $\ip{\I_{\cot(-\pi/d)}}_{\max} - O(d r\se)$, which are
	\begin{align}
		S_1 = \left(M_{\nr+1}, M_{\nr+2}, N_1, N_2, \frac{M_\ast^\diamond\ket{\psi}}{\norm{M_\ast^\diamond\ket{\psi}}}\right),\\
		S_2 = \left(N_{\nr+1}, N_{\nr+2}, M_1, M_2, \frac{M_\ast^\diamond\ket{\psi}}{\norm{M_\ast^\diamond\ket{\psi}}}\right).
	\end{align}
\end{proposition}

@@

To prove that $S_1$ achieve $\ip{\I_{\cot(-\pi/d)}}_{\max} - O(d r\se)$, we need to examine terms of the form
$\bra{\psi} M_\ast^\diamond M_{x}^aN_y^b M_\ast^\diamond\ket{\psi}$ for $x = \nr+1,\nr+2$, $y=1,2$ and $a,b = 0.1$,
which relate to $\bra{\psi} M_x^a N_y^b \ket{\psi}$ as follows,

@@

	   \bra{\psi} M_{x}^aN_y^b \ket{\psi} 
	= &\bra{\psi}(M_\ast^\diamond + M_\ast^\perp) M_x^a N_y^b (M_\ast^\diamond + M_\ast^\perp)\ket{\psi} \\
	= & \bra{\psi}M_\ast^\diamond M_x^aN_y^b M_\ast^\diamond\ket{\psi} + \bra{\psi}M_\ast^\diamond M_x^aN_y^b M_\ast^\perp\ket{\psi}\\
	&+\bra{\psi}M_\ast^\perp M_x^aN_y^b M_\ast^\diamond\ket{\psi} + \bra{\psi}M_\ast^\perp M_x^aN_y^b M_\ast^\perp\ket{\psi}\\
	\appd{O(r\se)}&  \bra{\psi}M_\ast^\diamond M_x^aN_y^b M_\ast^\diamond\ket{\psi} + \bra{\psi}M_\ast^\diamond M_x^aN_y^b M_x^\perp\ket{\psi} \\
	&+\bra{\psi}M_x^\perp M_x^aN_y^b M_\ast^\diamond\ket{\psi} + \bra{\psi}M_x^\perp M_x^aN_y^b M_x^\perp\ket{\psi}\\
	=&\bra{\psi}M_\ast^\diamond M_x^aN_y^b M_\ast^\diamond\ket{\psi},

@@

where we use the facts that $M_\ast^\perp \ket{\psi} \appd{O(r\se)} M_x^\perp \ket{\psi}$ and that 
$\supp(M_x^0) \cap \supp(M_x^\perp) = \emptyset$ for the relevant values of $(x,y,a,b)$.
This means that if Alice and Bob share state $M_\ast^\diamond \ket{\psi}/\norm{M_\ast^\diamond \ket{\psi}}$ and apply $M_{\nr+1}^0N_1^0$
they get conditional probability

@@

The rest of the conditional probabilities produced by $S_1$ can be derived in the same way.

@@

	Let $S$ be an $\ep$-approximate strategy of $\fC(d,r)$ and $M_{\nr+1}, M_{\nr+2},N_{\nr+1}$ and $N_{\nr+2}$ as defined in \cref{prop:s1s2}.

@@

	\textbf{To prove \cref{eq:psi1_eq}}, 
	recall that $M_{\nr+1}^0 \ket{\psi} \appd{O(r\se)} N_{\nr+1}^0 \ket{\psi}$ 
	and $M_{\nr+1}^1 \ket{\psi} \appd{O(r\se)} N_{\nr+1}^1 \ket{\psi}$ proved in \cref{prop:chsh_base},
	so it suffices to show
	$(M_{\nr+2}M_{\nr+1}^1 - M_{\nr+2}M_{\nr+1}^0) \ket{\psi}$ is close to $(- N_{\nr+2}N_{\nr+1}^1+N_{\nr+2}N_{\nr+1}^0)\ket{\psi}$,
%	or equivalently,
%	$M_{\nr+2}M_{\nr+1} \ket{\psi}$ is close to $-N_{\nr+2}N_{\nr+1} \ket{\psi}$.
	At this point, we can use the anti-commutation relation induced by $S_1$ (\cref{eq:zaxa}) and conclude that 
	\begin{align*}
		M_{\nr+1}M_{\nr+2} M_\ast^\diamond \ket{\psi} \appd{\frac{\norm{\ket{M_\ast^\diamond\ket{\psi}}}}{c\sqrt{s}}O(\sd\sr\qe)} -M_{\nr+1}M_{\nr+2} M_\ast^\diamond \ket{\psi}.
	\end{align*}
	Using the fact $c = 1 - \pi^2/(2d^2) + O(1/d^4)$ and $s = \pi/d + O(1/d^3)$, the distance above is of order $O(\sd \sr \qe)$.
	Then we can show that 
	\begin{align*}
		M_{\nr+2}M_{\nr+1}\ket{\psi} &= M_{\nr+2}M_{\nr+1}(M_{\nr+1}^0 + M_{\nr+1}^1)\ket{\psi} \\
			&\appd{O(r\se)} M_{\nr+2}M_{\nr+1} M_\ast^\diamond \ket{\psi} \\
			&\appd{O(\sd \sr \qe)} -M_{\nr+1}M_{\nr+2} M_\ast^\diamond \ket{\psi}\\
			&\appd{O(r\se)} -M_{\nr+1}M_{\nr+2} \ket{\psi} \\
			&\appd{O(r\se)} -M_{\nr+1} N_{\nr+2} \ket{\psi} \\
			&\appd{O(r\se)} -N_{\nr+2} N_{\nr+1} \ket{\psi}.
	\end{align*}
	The proof of $\ket{\psi_2} \appd{O(\sd \sr \qe)} \ket{\psi_4}$ is similar.

	\textbf{To prove \cref{eq:psi1_sum}}, we use the definition of $\ket{\psi_1}$ and $\ket{\psi_2}$ and get 
	\begin{align*}
		\ket{\psi_2} + \ket{\psi_1} = 1/2( 2M_{\nr+1}^0 + 2M_{\nr+1}^1) \ket{\psi} \appd{O(r\se)} M_\ast^\diamond \ket{\psi}.
	\end{align*}

	\textbf{To prove \cref{eq:psi1_orth}}, we expand the inner product and get 
	\begin{align*}
		&\braket{\psi_1}{\psi_2}\\
	 = &1/4\bra{\psi}(M_{\nr+1}^0 - iM_{\nr+1}^1M_{\nr+2} + iM_{\nr+1}^0M_{\nr+2} +M_{\nr+1}^1)\\
	 &(M_{\nr+1}^1 + iM_{\nr+2}M_{\nr+1}^0 -iM_{\nr+2}M_{\nr+1}^1 + M_{\nr+1}^0)\ket{\psi}\\
	 =& 1/2i \bra{\psi}(M_{\nr+1}^0M_{\nr+2}M_{\nr+1}^0-M_{\nr+1}^1M_{\nr+2}M_{\nr+1}^1\ket{\psi}.
	\end{align*}
	Then we will show that $\bra{\psi} M_{\nr+1}^0M_{\nr+2}M_{\nr+1}^0 \ket{\psi} \appd{O( r\se)} 0$ as follows
	\begin{align*}
	 \bra{\psi}(M_{\nr+1}^0M_{\nr+2}M_{\nr+1}^0\ket{\psi} &\appd{O(r\se)}  \bra{\psi}(N_{\nr+1}^0M_{\nr+2}N_{\nr+1}^0)\ket{\psi}\\
	  &=\bra{\psi}M_{\nr+2}N_{\nr+1}^0)\ket{\psi}\\
	&\appd{O(r^2\ep)} 0,
	\end{align*}
	where the last approximation comes from the correlation.
	Similarly, we have 
	\begin{align*}
	\bra{\psi}(M_{\nr+1}^1M_{\nr+2}M_{\nr+1}^1\ket{\psi} \appd{O(r\se)} \bra{\psi} M_{\nr+2}N_{\nr+1}^1 \ket{\psi} \appd{O(r^2\ep)} 0.
	\end{align*}
	Hence, $\braket{\psi_2}{\psi_1} \appd{O(r\se)} 0$.

@@

        		&= (\cos(\frac{2\pi}{d}) M_{\nr+1}^0 - \sin(\frac{2\pi}{d}) M_{\nr+2}M_{\nr+1}^1)\ket{\psi}.

@@

        		&= (\cos(\frac{2\pi}{d}) M_{\nr+1}^1 + \sin(\frac{2\pi}{d}) M_{\nr+2}M_{\nr+1}^0)\ket{\psi},

@@

We use this observation in the proof of the following lemma.

@@
